NFC and burnout in teachers - A replication and extension study

### 2021-10-29 Manuscript/Manuscript.Rmd
updated explor2 model and wrote results

  # structural model
    COVB ~ YEARS
    SCS ~ YEARS
    NFC ~~ SCS
    NFC ~~ COVB
    DTH ~ COVB + SCS + NFC
    DRF ~ SCS + NFC
    DTH ~~ DRF
    MBI_EE ~ DTH + COVB
    MBI_RPE ~ DRF

@@

    drf1 ~~ drf2
    drf1 ~~ drf3
    drf2 ~~ drf3
'

@@

>>>>

  # structural model
    COVB ~ yc * YEARS
    SCS ~ ys * YEARS
    NFC ~~ SCS
    NFC ~~ COVB
    DTH ~ cdth * COVB + sdth * SCS + ndth* NFC
    DRF ~ sdrf * SCS + ndrf * NFC
    DTH ~~ DRF
    MBI_EE ~ dthe * DTH + ce * COVB
    MBI_RPE ~ drfr * DRF

@@

    drf1 ~~ drf2
    drf1 ~~ drf3
    drf2 ~~ drf3

  # Indirect effects
    Indirect1 := (ndrf * drfr) + (ys * sdrf * drfr)
    Indirect2 := (ndth * dthe) + (ys * sdth * dthe) + (yc * cdth * dthe)

  # contrast (if significant, the effects differ)
    Contrast := Indirect1 - Indirect2

  # total effect
    Total := (ndrf * drfr) + (ys * sdrf * drfr) + (ndth * dthe) + (ys * sdth * dthe) + (yc * cdth * dthe)
'

@@

The second exploratory analysis concerned the incorporation of the Covid burden score into the model.
We based the development of this model on the partial correlations of all variables, which provide an indication of how closely or remotely related variables might be in a path model.
Then we modified the structure of the model in order to increase the goodness-of-fit indices within the framework of contentually meaningful variable relationships.
The final model is illustrated in **Figure**, the total, direct, and indirect effects are listed in **Supplementary Table**.
All fit indices suggest that the proposed model has good fit while the baseline model does not ($\chi^2=$`r round(fit_explor2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), $CFI=$`r round(fit_explor2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, $RMSEA=$`r round(fit_explor2_summ[["FIT"]][["rmsea.robust"]], digits = 2)` (95% $CI$ [`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`]), $SRMR=$`r round(fit_explor2_summ[["FIT"]][["srmr"]], digits = 2)`).
Neither the ERQ sum score, nor its subscales, nor the depersonalisation subscale of the MBI contributed significantly to the explained variance and were therefore not included in the final model.
Years spent teaching was associated with higher self control ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ys"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ys"], digits = 3)`) and higher Covid burden ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "yc"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "yc"], digits = 3)`) but not with NFC.
NFC covaried with self control ($\sigma_{NFC,SCS}=$`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "SCS"], digits = 3)`) and Covid burden ($\sigma_{NFC,COVB}=$`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "COVB"], digits = 3)`), but not with years spent teaching ($p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$lhs == "NFC" & fit_explor2_summ$PE$op == "~~" & fit_explor2_summ$PE$rhs == "YEARS"], digits = 3)`).
In turn, NFC was associated with higher DRF scores ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndrf"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndrf"], digits = 3)`) and lower DTH scores ($\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "ndth"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "ndth"], digits = 3)`) but not directly with any of the two MBI subscales.
DRF scores fully mediated the negative association of NFC and self control with reduced personal efficacy (indirect effect $\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect1"], digits = 3)`), which was also true for DTH scores and emotional exhaustion, but DTH also partially mediated between Covid burden and emotional exhaustion (indirect effect $\beta = $`r round(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label == "Indirect2"], digits = 2)`, $p = $`r round(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label == "Indirect2"], digits = 3)`).
Covid burden was not associated with DRF or reduced personal efficacy.
